Fail Faster

### 2025-03-22 paper/paper.tex
wibble

\subsubsection{\scalaname}
In \scalaname, we implement a subset of the \camlname
strategies: the boolean list generator, single-pass BST generator, and
well-typed STLC term generator\footnote{By default, ScalaCheck does not support type derivation,
so those strategies are excluded.}. We did not implement an optimized version of ScalaCheck's
\rand, but our experimental setup was otherwise the same as in \secref{subsubsection:ocaml}.

>>>>

\subsubsection{\scalaname}
In \scalaname, we implement a subset of the \camlname
strategies: the boolean list generator, single-pass BST generator, and
well-typed STLC term generator\footnote{By default, ScalaCheck does not support deriving gnenerators from types,
so those strategies are excluded.}. We did not implement an optimized version of ScalaCheck's
\rand, but our experimental setup was otherwise the same as in \secref{subsubsection:ocaml}.
